---
title: "Getting started with parfor"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started with parfor}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This function is adapted from the excellent `foreach::foreach` package. The difference is: `misc::parfor` calls a function in a loop. Two of the advantages of `misc::parfor` over `foreach::foreach` are: 

- you **don't have to register a parallel backend** before using it. Just specify `cl` to use parallel processing.
  
- you can directly **monitor the progress of the parallel computation with a progress bar**.
   

```{r}
library(misc)
```

```{r}
misc::parfor(function(x) x^2, 1:10)
```

```{r}
misc::parfor(function(x) x^2, 1:10, cl = 2)
```

```{r}
misc::parfor(function(x) x^2, 1:10, verbose = TRUE)
```

```{r}
misc::parfor(function(x) x^3, 1:10, show_progress = FALSE)
```

```{r}
misc::parfor(function(x) x^3, 1:10, show_progress = FALSE)
```

```{r}
foo <- function(x)
{
  print(x)
  return(x*0.5)
}
misc::parfor(foo, 1:10, show_progress = FALSE, 
verbose = TRUE, combine = rbind)
```

```{r}
misc::parfor(foo, 1:10, show_progress = FALSE, 
verbose = TRUE, combine = cbind)
```

```{r}
foo2 <- function(x)
{
  print(x)
  return(x*0.5)
}
misc::parfor(foo2, 1:10, show_progress = FALSE, 
verbose = TRUE, combine = '+')
```
